Placeholder for article 3

### 2025-01-21 analysis/paper/paper.qmd
Small changes do main doc, template + render
TL table with classes to understand how this specific group of cherts relates to the technological variables.

ggpubr::ggarrange(proto_scatter, proto_stats_weight, labels = c("b1", "b2"), ncol = 2, common.legend = TRUE, legend = "bottom")

@@

>>>>

ggpubr::ggarrange(proto_scatter, proto_stats_weight, labels = c("a", "b"), ncol = 2, common.legend = TRUE, legend = "bottom")

@@

```{r}
#| label: tbl-TL-classes
#| tbl-cap: Trace lithologies cherts from the Gravettian and Proto-Solutrean assemblages of the Terrace and Solutrean assemblage from the Shelter and corresponding technological class.

TL_classes_terrace <- phase_dataset |> 
  filter(RMTYPE == "TL") |> 
  select(Technocomplex, SUBTYPE, ID, CLASS, RETOUCHEDPIECETYPOLOGY)

TL_classes_shelter <- solutrean_dataset |> 
  mutate(Technocomplex = case_when(
    LEVEL == "A" | LEVEL == "B" | LEVEL == "C" ~ "Solutrean")) |> 
  filter(RMTYPE == "TL") |> 
  select(Technocomplex, SUBTYPE, ID, CLASS, RETOUCHEDPIECETYPOLOGY)

TL_classes <- rbind(TL_classes_terrace, TL_classes_shelter)
TL_classes <- TL_classes |> 
  rename(TL = SUBTYPE) |> 
  arrange(TL)

kable(head(TL_classes))
